Build azimuth compatible fetal kidney reference from the kidney cell atlas

### 2024-08-14 analyses/cell-type-wilms-tumor-06/00_fetal_reference_kidney.Rmd
add to PR #706
switch to selfcontained mode to render the plots

---
title: "Build azimuth compatible fetal kidney reference from the kidney cell atlas"
author: "Maud PLASCHKA"
date: '2024-08-07'
params:
  ref_url: "https://datasets.cellxgene.cziscience.com/40ebb8e4-1a25-4a33-b8ff-02d1156e4e9b.rds"
  padj_threshold: 0.05
  lfc_threshold: 1
  rate1_threshold: 0.5
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

```{r path_to_data}
path_to_data <- file.path(module_base, "scratch", fetal_full.rds")

>>>>

---
title: "Build azimuth compatible fetal kidney reference from the kidney cell atlas"
author: "Maud PLASCHKA"
date: '2024-08-07'
params:
  ref_url: "https://datasets.cellxgene.cziscience.com/40ebb8e4-1a25-4a33-b8ff-02d1156e4e9b.rds"
  padj_threshold: 0.05
  lfc_threshold: 1
  rate1_threshold: 0.5
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
    self_contained: yes
    mode: selfcontained
---

@@

```{r path_to_data}
path_to_data <- file.path(module_base, "scratch", "fetal_full.rds")
